---
title: "Data_Analysis_Kaggle"
author: "Rick SCHNEIDER"
date: "November 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this file is to study:
1) Study and analyse the air_reserve data set
2) Study the relation between air and hpg using the store_id_relation data set

-----------------------------------------------------------------------------------

1) Analysis of "air_reserve"

```{r}
#libraries:
library(dplyr)
library(ggplot2)
```

```{r}
#Load data
air <- read.csv("data/air_reserve.csv")
```

First, lets get a general idea of the data:
```{r}
View(air)
dim(air)
names(air)
glimpse(air)
sum(is.na(air))
```
This file provides information on the reservations that have been made through the air. It has 92.378 rows and 4 columns, i.e. the store id ON THE AIR SYSTEM, the visit time, the reserve time (date and time), and the number of people the reservation has been done for. 
-Apparently, no missing values (at least not properly encoded ones)


```{r}
#How many different stores:
air %>% distinct(air_store_id) %>% summarize(n())
#Number of visits per store:
store_count <- air %>% 
                  group_by(air_store_id) %>% 
                  summarize(count=sum(reserve_visitors))
summary(store_count$count)
View(store_count)
```
-There are 314 different stores with an average of 1318 visits, and a median of 808 visits. The min being 1 visit (no obvious outlier) and the max being 8355 (very popular restaurant on that platform).


```{r}
#Transformation in date time:
#visit time:
air$visit_datetime <- as.POSIXct(air$visit_datetime)
summary(air$visit_datetime)
#reserve time:
air$reserve_datetime <- as.POSIXct(air$reserve_datetime)
summary(air$reserve_datetime)
```

The first reservation has been made on the first of january, and the last reservation on the 22 of april.
The first visit happened the first of january as well, and the last visit on the first of mai.
This is important to know as we want to predict "the future", so our test/train split has to be done accordingly! (e.g. train:01.01.16 - 01.01.17, test: 02.01.17 - 05.01.17, as we want to predict future months!).