---
title: "project"
author: "Alexis Laks"
date: "3 novembre 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(lubridate)
library(timeDate)
```

```{r}
reserve_air <- read_csv("data/air_reserve.csv")
reserve_air %>% dim()
reserve_air %>% names()
reserve_air %>% class()
reserve_air %>% summary()
reserve_air %>% head()
reserve_air %>% distinct(air_store_id) %>% nrow()

c(min(reserve_air$visit_datetime),max(reserve_air$visit_datetime)) ## Checking out timeinterval
reserve_air <- reserve_air %>% mutate(vars(visit_datetime,reserve_datetime), ymd_hms()) # changing time format although it may be they are already in date-time format. 


reserve_hpg <- read_csv("data/hpg_reserve.csv")
reserve_hpg %>% dim()
reserve_hpg %>% names()
reserve_hpg %>% class()
reserve_hpg %>% summary()
reserve_hpg %>% distinct(hpg_store_id) %>% nrow() 

c(min(reserve_hpg$visit_datetime),max(reserve_hpg$visit_datetime))
reserve_hpg <- reserve_hpg %>% mutate(visit_datetime = ymd_hms(visit_datetime)) %>% mutate(reserve_datetime = ymd_hms(reserve_datetime))
```

13325 different restaurants reserved with hpg vs. 314 with air. In these 2 data sets we have the time of reservation and time of visit as well as number of visitors for each restaurant in each of the platforms. The time interval considered in both datasets is from the first of January 2016 to the 31st of May 2017.
So both datasets have the same structure and are on the same time interval. Convenient. Let's look at our other data;

```{r}
visit_air <- read_csv("data/air_visit_data.csv")
visit_air %>% glimpse()
visit_air %>% distinct(air_store_id) %>% nrow()
c(min(visit_air$visit_date),max(visit_air$visit_date)) 
```

Here data is approx the same, although misses out on a whole month of may 2017. We get the number of visits in total, so we can get a number of no-reservation visits by joining the two data sets and substractng the total nb of visits and nb of visits with reservation done on hpg. 


```{r}
store_air <- read_csv("data/air_store_info.csv")
store_air 
levels(as.factor(store_air$air_genre_name))
```


```{r}
store_hpg <- read_csv("data/hpg_store_info.csv")
store_hpg
levels(as.factor(store_hpg$hpg_genre_name))
```

In the "store" data sets we get the cuisine style for each restaurant that was booked in each of the dataset. 

```{r}
holidays <- read_csv("data/date_info.csv")
holidays
```

date info just flags which dates correspond to specific holidays where we could expect a higher number of visits. If the effect is significant we should indeed take into account. 

Let's check for any missing values in our data:
```{r}
sum(is.na(c(reserve_air,store_air,visit_air,reserve_hpg,store_hpg,holidays)))
```
No na's which saves a lot of time. The main issue here when trying to create a prediction is 1. dealing with times series, and 2. dealing with different lengths of data both store-wise and time-wise. 

```{r}
c(min(reserve_air$visit_datetime),max(reserve_air$visit_datetime)) 
c(min(reserve_hpg$visit_datetime),max(reserve_hpg$visit_datetime)) 
c(min(visit_air$visit_date),max(visit_air$visit_date)) # visit air contains smaller time serie
```

# EDA

## Visit trends:

### visit_air

*To what correspond this data compared to reserve_air??*

Let's see how many visits we got over the time frame in our air data:
```{r}
visit_air %>%
  group_by(visit_date) %>%
  summarise(all_visitors = sum(visitors)) %>%
  ggplot(aes(visit_date,all_visitors)) +
  geom_line(col = "blue") +
  labs(y = "All visitors", x = "Date", title = "nb of visits form January 2016 to May 2017")
```

Seems the number of visits climbed July 2016 and haven't gone done since, except for one spike which corresponds to new years eve. What we can also see is there almost constant fluctuation in nb of visits, which surely corresponds to week-days vs. week-ends. 
For further insight, we can check how common it is to get a specific number of visitors per day. 

```{r}
visit_air %>%
  ggplot(aes(visitors)) +
  geom_vline(xintercept = 20, color = "orange") +
  geom_histogram(fill = "blue", bins = 30) +
  scale_x_log10()
```

Ok so the most common amount of visitors in a random restaurant per day is 20, but how does that evolve in a week? We saw constant fluctuations in the week that made us think e

```{r}
visit_air %>%
  mutate(wday = wday(visit_date, label = TRUE)) %>%
  group_by(wday) %>%
  ggplot(aes(wday, visits, fill = wday)) +
  geom_col() +
  theme(legend.position = "none", axis.text.x  = element_text(angle=45, hjust=1, vjust=0.9)) +
  labs(x = "Day of the week", y = "average nb of visitors per day per restaurant")
```

As expected, week-ends are more charged than week days, rising on fridays, peak on saturdays then gowing back on sundays to monday. We can check for trends month-wise also, although as holidays are a bit distributed randomly throughought the year we shouldn't see any striking patterns, except maybe for summer months and december.

```{r}
visit_air %>%
  mutate(month = month(visit_date, label = TRUE)) %>%
  group_by(month) %>%
  summarise(visits = mean(visitors)) %>%
  ggplot(aes(month, visits, fill = month)) +
  geom_col() +
  theme(legend.position = "none") +
  labs(x = "Month", y = "Mean visitors per month")
```

As expected, December sees more visitors than usual, although there isn't a summer-trend we expected. Seems as though Spring rather is a season where visits are higher than usual. 

### reserve_air

```{r}
reserve_air_1 <- reserve_air %>%
  mutate(reserve_date = date(reserve_datetime), # Date of reservation
         reserve_hour = hour(reserve_datetime), # Hour of reservation
         reserve_wday = wday(reserve_datetime, label = TRUE), # Day of reserveration (lun,mar..)
         visit_date = date(visit_datetime), # Date of visit
         visit_hour = hour(visit_datetime), # Hour of visit
         visit_wday = wday(visit_datetime, label = TRUE), # Day of visit
         diff_hour = time_length(visit_datetime - reserve_datetime, unit = "hour"), # hours btw res and vis
         diff_day = ceiling(time_length((visit_datetime - reserve_datetime), unit = "day")) # days btw " "
         )
reserve_air_1
```

Let's check the patterns in fluctuations of visitors in the restaurants in our air dataset:

```{r}
reserve_air_1 %>%
  group_by(visit_date) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_date, all_visitors)) +
  geom_line() +
  labs(x = "'air' visit date")
```

Here two things come out: One, there is a considerable increase in number of visitors from july onward (so either it's an increase of the nb of restaurants in the air platform or people in japan suddenly started going to restaurants more) 
Two, There is a whole time period where there are 0 entries. So there weren't any na's but there was still missing data. 

Since we have the hours of visits in our reserve air dataset, we can check when is the most common time for visitors (should be in the evening and around noon)

```{r}
reserve_air_1 %>%
  group_by(visit_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_hour, all_visitors)) +
  geom_col(fill = "blue") +
  labs(title = "nb of visitors per hour of the day")
```

So surprisingly there are very few visitors at noon, although there is a slight increase. But the bulk of the visitors seem to come around 7 to 8 pm. We have also info on the time the reservation was made, and the time of the visit, which gives us an idea of how customers plan their restaurant ahead. 

```{r}
reserve_air_1 %>%
  filter(diff_hour < 24*5) %>%
  group_by(diff_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(diff_hour, all_visitors)) +
  geom_col(fill = "blue") +
  labs(x = "Time between reservation and visit under 5 days")
```

Here we can see that the vast majority of customers will either call a few hours from their reservation (most even 1 hour before) or in general will call n*24 hours before their visit. 

```{r}
max(reserve_air_1$diff_day) ## seems there are people who reserved more than a year before their visit...
reserve_air_1 %>%
  arrange(desc(diff_day)) %>%
  group_by(diff_day) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot() +
  aes(x = diff_day, y = all_visitors) +
  geom_col(fill = "blue") +
  labs(x = "Time between reservation and visit") +
  scale_y_log10()
```

Seems there a few fancy restauratns that are constantly overbooked where people make reservation months even a year before visiting. 

### hpg data:

Same as with the air data, let's look at how it is distributed:

```{r}
reserve_hpg_1 <- reserve_hpg %>%
  mutate(reserve_date = date(reserve_datetime), # Date of reservation
         reserve_hour = hour(reserve_datetime), # Hour of reservation
         reserve_wday = wday(reserve_datetime, label = TRUE), # Day of reserveration (lun,mar..)
         visit_date = date(visit_datetime), # Date of visit
         visit_hour = hour(visit_datetime), # Hour of visit
         visit_wday = wday(visit_datetime, label = TRUE), # Day of visit
         diff_hour = time_length(visit_datetime - reserve_datetime, unit = "hour"), # hours btw res and vis
         diff_day = ceiling(time_length((visit_datetime - reserve_datetime), unit = "day")) # days btw " "
         )
reserve_hpg_1
```

Let's check the patterns in fluctuations of visitors in the restaurants in our air dataset:

```{r}
reserve_hpg_1 %>%
  group_by(visit_date) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_date, all_visitors)) +
  geom_line() +
  labs(x = "'air' visit date")
```

Here two things come out: One, there is a considerable increase in number of visitors from july onward (so either it's an increase of the nb of restaurants in the air platform or people in japan suddenly started going to restaurants more) 
Two, There is a whole time period where there are 0 entries. So there weren't any na's but there was still missing data. 

Since we have the hours of visits in our reserve air dataset, we can check when is the most common time for visitors (should be in the evening and around noon)

```{r}
reserve_hpg_1 %>%
  group_by(visit_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_hour, all_visitors)) +
  geom_col(fill = "blue") +
  labs(title = "nb of visitors per hour of the day")
```

So surprisingly there are very few visitors at noon, although there is a slight increase. But the bulk of the visitors seem to come around 7 to 8 pm. We have also info on the time the reservation was made, and the time of the visit, which gives us an idea of how customers plan their restaurant ahead. 

```{r}
reserve_hpg_1 %>%
  filter(diff_hour < 24*5) %>%
  group_by(diff_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(diff_hour, all_visitors)) +
  geom_col(fill = "blue") +
  labs(x = "Time between reservation and visit under 5 days")
```

Here we can see that the vast majority of customers will either call a few hours from their reservation (most even 1 hour before) or in general will call n*24 hours before their visit. 

```{r}
max(reserve_hpg_1$diff_day) ## seems there are people who reserved more than a year before their visit...
reserve_air_1 %>%
  arrange(desc(diff_day)) %>%
  group_by(diff_day) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot() +
  aes(x = diff_day, y = all_visitors) +
  geom_col(fill = "blue") +
  labs(x = "Time between reservation and visit") +
  scale_y_log10()
```

Seems there a few fancy restauratns that are constantly overbooked where people make reservation months even a year before visiting. 
