---
title: "Algorithm"
author: "Rick SCHNEIDER"
date: "November 26, 2018"
output: html_document
---

```{r}
library(dplyr)
library(tidyr)
library(data.table)
```


This file will be divided into 3 section:
1)generate a csv-file merging all the data from air into one file
2)generate a csv-file that merges all the data we have from Kaggle into 1 file
3)generate the sample submission data set in order to create our prediction

----------------------------------------------------------------------------------------------------------------
1)


# AIR :

While looking at this I found something weird, since we decided not to use the reservation info since we can't get them from the sample submission, we only need the air_visit_data and air_store_info and potentially the HPG data if we assume that the reserve visitors actually correspond to the real visitors (everyone showed up !)

## Without reserve info :

### Adding store info

```{r}
air_store_info <- fread("data/air_store_info.csv")
air_visit_data <- fread("data/air_visit_data.csv")
air_data <- full_join(air_visit_data,air_store_info, by = "air_store_id") %>%
  rename(id = air_store_id) %>%
  rename(genre_name = air_genre_name) %>%
  rename(area_name = air_area_name)

summary(is.na(air_data)) # No NA's.
```

### Adding date info

```{r}
date_info <- fread("data/date_info.csv")
date_info <- date_info %>%
  rename(visit_date = calendar_date)

air_data <- left_join(air_data,date_info,by="visit_date") %>%
  rename(day_of_the_week_visit = day_of_week) %>%
  rename(holiday_flg_visit = holiday_flg) # CAREFULL, here it's an inner join, some days there were just no restaurants open

summary(is.na(air_data)) # No NA's.
names(air_data)

```


### Generate excel file:

export and output as air_data.csv
```{r}
write.csv(air_data, file="data/air_data.csv", row.names = FALSE) 
final_data <- read.csv("data/complete_data.csv")
View(air_data)
air_data %>% distinct(genre_name)
```







----------------------------------------------------------------------------------------------------------------
2)

Load all the data in
```{r}
air_reserve <- read.csv("data/air_reserve.csv")                   #check
air_store_info <- read.csv("data/air_store_info.csv")             #check
air_visit_data <- read.csv("data/air_visit_data.csv")             
data_info <- read.csv("data/date_info.csv")                       #check
hpg_reserve <- read.csv("data/hpg_reserve.csv")                   #check
hpg_store_info <- read.csv("data/hpg_store_info.csv")             #check
store_id_relation <- read.csv("data/store_id_relation.csv")       #check
sample_submission <- read.csv("data/sample_submission.csv")
```


First, we are going to add the hpg_reserve (with changed hpg ids to air ids) to the air_reserve, and call the data set global:
```{r}

#rename to id:
air_reserve <- air_reserve %>% rename(id = air_store_id)
hpg_reserve <- hpg_reserve %>% rename(id = hpg_store_id)


#paste them together:
reserve <- rbind(air_reserve, hpg_reserve)

```

Now, we need to add air_store_info and hpg_store_info.

```{r}
glimpse(air_store_info)
glimpse(hpg_store_info)
```

```{r}
#rename to id:
air_store_info <- air_store_info %>% 
                    rename(id = air_store_id,
                           genre_name = air_genre_name,
                           area_name = air_area_name)
hpg_store_info <- hpg_store_info %>% 
                    rename(id = hpg_store_id,
                           genre_name = hpg_genre_name,
                           area_name = hpg_area_name)

#paste them together:
info <- rbind(air_store_info, hpg_store_info)

nrow(info)
nrow(reserve)

info %>% filter(id %in% reserve$id) %>% summarize(n())
reserve %>% filter(id %in% info$id) %>% summarize(n())
```
At this point, we have not generated NA's yet (which is normal, as we have not merged the data sets, and the csv files that we got have no missing values).

Now we need to merge reserve and info on id:

```{r}
#final <- full_join(reserve,info,by="id")
final <- inner_join(reserve,info,by="id")

nrow(final)

colSums(is.na.data.frame(final))

#View(final)
```
We do an inner join, as a full_join will create a huge chunk of missing data, and will create a data set that will not be helpful for the prediction. We would need to adapt a whole stretegy to those NA's, and imputng them would not make much sense, as we do not have enough data to predict/impute them well.


Data info:

```{r}
glimpse(final)
glimpse(data_info)
```
 
Join it on the calender date:
```{r}
data_info <- data_info %>% 
                    rename(visit_date= calendar_date)

final <-final %>% 
                separate(visit_datetime, into = c('visit_date', 'visit_time'), sep = 10) %>% 
                separate(reserve_datetime, into = c('reserve_date', 'reserve_time'), sep = 10)

#join, as we do not want to loose data here!
final <- full_join(final,data_info,by="visit_date")

#rename
final <- final %>% 
            rename(day_of_the_week_visit = day_of_week,
                   holiday_flg_visit = holiday_flg)

#for reserve:
data_info <- data_info %>% 
                    rename(reserve_date= visit_date)
final <- full_join(final,data_info,by="reserve_date")
#rename
final <- final %>% 
            rename(day_of_the_week_reserve= day_of_week,
                   holiday_flg_reserve = holiday_flg)

#View(final)

```

This last operation created 39 rows with only NA's!, they only contain dates, and should therefore be deleted.
```{r}
colSums(is.na.data.frame(final))
nrow(final)                          #963.725
final <- drop_na(final)              #963.686
nrow(final)
colSums(is.na.data.frame(final))
```


```{r}
#join on store_id_relation and change names of hpg to air
store_id_relation <- store_id_relation  %>% 
                    rename(id = hpg_store_id)
final3 <- full_join(final, store_id_relation, by= "id")
ind <- !is.na(final3[,"air_store_id"])
final3[ind,"id"] <- as.character(final3[ind,"air_store_id"])

final3 <- final3 %>% select(-air_store_id)

colSums(is.na.data.frame(final3))

glimpse(final3)

nrow(final3)

#get rid of 87 columns with NAs in visit_date:
ind <- is.na(final3$visit_date)
final3 <- final3[!ind,]
```


```{r}
glimpse(air_visit_data)

air_visit_data <- air_visit_data %>% 
                    rename(id = air_store_id)
glimpse(final3)

final2 <- full_join(final3,air_visit_data,by=c("id","visit_date"))
glimpse(final2)
colSums(is.na.data.frame(final2))
```




Merge with the sample submission file:
```{r}
#split date from id:  
sample_submission <- sample_submission %>% 
                        separate(id, into = c("id","predict_date"), sep=20)  

sample_submission <- sample_submission %>% 
                        separate(predict_date, into = c("error","predict_date"), sep=1) 

sample_submission <- sample_submission %>% 
                        select(-error)


glimpse(sample_submission)
glimpse(final_data)
#join sample_submission with data:
nrow(sample_submission)
nrow(final_data)
complete_sample <- sample_submission %>% filter(id %in% final_data$id)
nrow(complete_sample)

glimpse(complete_sample)


complete_data <- left_join(sample_submission,final_data, by="id")
glimpse(complete_data)
complete_data <- complete_data %>% distinct(id,predict_date)

complete_data <- complete_data %>% 
                  select(-c(visitors.x,visit_date,visit_time,reserve_date,reserve_time,reserve_visitors,day_of_the_week_visit,holiday_flg_visit,day_of_the_week_reserve,holiday_flg_reserve,visitors.y))


```



final3 is the complete data set, it is exported in a csv file!
create a csv file:
```{r}
write.csv(final2, file="data/complete_data.csv", row.names = FALSE) 
final_data <- read.csv("data/complete_data.csv")

```


----------------------------------------------------------------------------------------------------------------

3)

```{r}
View(air_data_c)
air_data_c <- air_data

air_data_c <- air_data_c %>% select(-c(visitors,visit_date,day_of_the_week_visit,holiday_flg_visit))
  
join <- air_data_c[air_data_c$id %in% sample_submission$id,]
join <- join %>% distinct(id,genre_name,area_name,latitude, longitude)

complete <- left_join(sample_submission,join,by="id")
View(data_info)
data_info <- data_info %>% rename(predict_date=reserve_date)
complete2 <- left_join(complete,data_info,by="predict_date")
sum(is.na.data.frame(complete2))
View(complete2)
write.csv(complete2, file="data/submission_data.csv", row.names = FALSE) 
```





